\documentclass[8pt]{article}

\usepackage{graphicx}
\usepackage{amsmath,amsfonts,amsthm,amssymb}
\usepackage[margin=.9in]{geometry}
%\topmargin=-0.45in      %
%\evensidemargin=0in     %
%\oddsidemargin=0in      %
%\textwidth=6.5in        %
%\textheight=9.0in       %
%\headsep=0.25in         %


\newcommand{\ans}[1]
  {\noindent\fbox{\begin{minipage}[c]{\columnwidth}#1\end{minipage}}}


\newcommand{\ip}[1]{\left\langle #1 \right\rangle}
\newcommand{\torus}{\mathbb{T}}
\newcommand{\RRR}{\mathbb{R}}
\newcommand{\NNN}{\mathbb{N}}
\newcommand{\ZZZ}{\mathbb{Z}}
\newcommand{\QQQ}{\mathbb{Q}}
\newcommand{\CCC}{\mathbb{C}}
\newcommand{\HHH}{\mathcal{H}}
\newcommand{\FFF}{\mathcal{F}}

\newcommand{\B}[1]{\mathbf{ #1 }}



\makeatletter
\newcommand{\V}[2][r]{%
  \gdef\@VORNE{1}
  \left[\hskip-\arraycolsep%
    \begin{array}{#1}\vekSp@lten{#2}\end{array}%
  \hskip-\arraycolsep\right]}

\def\vekSp@lten#1{\xvekSp@lten#1;vekL@stLine;}
\def\vekL@stLine{vekL@stLine}
\def\xvekSp@lten#1;{\def\temp{#1}%
  \ifx\temp\vekL@stLine
  \else
    \ifnum\@VORNE=1\gdef\@VORNE{0}
    \else\@arraycr\fi%
    #1%
    \expandafter\xvekSp@lten
  \fi}
\makeatother






\begin{document}

\begin{center}
\textbf{Program 1 Feedback}
\end{center}

Hello all, I just finished grading your Programming one assignments and while most of you got the gist of the assignment many of your reports had problems with readability and organization.

The following are a list of things I'd like you to pay attention to when turning in your future assignments.  

Recall that style counts for about 20 \% of your grades on these assignments so it is IMPORTANT that you follow them.  I graded easily on style this time, but in the future will take off points if you don't follow the below criteria.

 
Organization

-Arrange your work in the following fashion

problem 1
 #1 analysis
 #1 programming code
 #1 results
 
 problem 2
 #2 analysis
 #2 programming code
 #3 results
 
 and so on.  A reader should not have to search your entire report to find the answer to one problem.
 
 
 - When discussing results from your code make sure that the results displayed close by.  You should not have a discussion of results on page 1 when the results are listed on page 10.  
 
 
 
 
 Analysis
 
 - You do not need to derive a method or show proofs for things done in class.  When using a method in the assignment state it in a concise manner.
 
 For example you if using Euler's Method you would say something like
 
 "Euler's Method is a O(h) accurate method given by
 \[
 y_{i+1} = y_i + h*f(y_i, t_i)
 \]
" 
 
 The point of these assignments is for you to use these methods, not to derive them.
 
 -  If you do not know how to typeset mathematics it is ok to leave a blank space and write the math in by hand.
 
 This is an example of what should NOT be done
 
"we solve the equation differential equation dy/dx = 4yx by separation of variables, first we multiply both sides by dx to get dy = 4y x dx then we divide both sides by y to get 1/y dy = 4 x dx and then we integrate to get ln(y) = 2x^2, then we exponential both sides to get y = e^(2x^2)"

Nobody wants to read this.
























\end{document}
